### 2020-08-25 manuscript/PLOS-MSc-Thesis.tex
change abstract introduction to morphogen and GRNs

\subsection*{Background}
A central problem in developmental and synthetic biology is to understand the 
mechanisms by which cells in a tissue or in a petri dish process external cues 
and transform such information into a coherent response, e.g. a terminal 
differentiation state. It has been stated that a gradient of concentration of 
certain molecule is enough to provide such positional information and produce 
cell differentiation by interacting with the cell's gene regulatory networks 
(GRNs).

>>>>

\subsection*{Background}
A central problem in developmental and synthetic biology is to understand the 
mechanisms by which cells in a tissue or in a petri dish process external cues 
and transform such information into a coherent response, e.g. a terminal 
differentiation state. It was long believed that this type of positional 
information could be entirely attributed to a gradient of concentration of a 
certain signaling molecule (i.e. a morphogen). However, advances in experimental 
methodologies and computer modeling have demonstrated the crucial role of the 
dynamics of a cell's gene regulatory network (GRN) in decoding the information 
carried by the morphogen, which is eventually translated into a spatial 
pattern. This morphogen interpretation mechanism has gained a lot of attention 
in systems biology as a tractable system to investigate the emergent properties 
of complex genotype-phenotype maps.
